---
title: "Demo of the Slidify Capability"
author: "Kevin A. Ryan"
output:
  html_document:
    highlight: monochrome
    theme: journal
hitheme: tomorrow
job: The Johns Hopkins University - Applied Physics Lab
highlighter: hprettify

framework: io2012
widgets:
- mathjax
- quiz
---

####A short Example based on World Bank Data 

### why reproducible research?

make a slidify version to demonstrate the capability!!!

***why reproducible research***

What reproducible reporting is about is a validation of the data analysis. Because you're not collecting independent data using independent methods, it's a little bit more difficult to validate the scientific question itself. But if you can take someone's data and reproduce their findings, then you can, in some sense, validate the data analysis. *This involves having the data and the code because more likely than not, the analysis will have been done on the computer using some sort of programming language, like R.* So you can take their code and their data and reproduce the findings that they come up with. Then you can at least have confidence that the analysis was done appropriately and that the correct methods were used.

###Motion Chart Prototype

Step 1: Get and wrangle data from World Bank
```{r, cache=TRUE}
  library (RJSONIO)
getWorldBankData <- function(id='SP.POP.TOTL', date='1960:2010', value="value", per.page=12000){ 
     
        url <- paste("http://api.worldbank.org/countries/all/indicators/", id,
                     "?date=", date, "&format=json&per_page=", per.page,
                     sep="")
        
        wbData <- fromJSON(url)[[2]]
        
        wbData = data.frame(
                year = as.numeric(sapply(wbData, "[[", "date")), 
                value = as.numeric(sapply(wbData, function(x)
                        ifelse(is.null(x[["value"]]),NA, x[["value"]]))),  
                country.name = sapply(wbData, function(x) x[["country"]]['value']),
                country.id = sapply(wbData, function(x) x[["country"]]['id'])    
        )
        
        names(wbData)[2] <- value
        
        return(wbData)
}

getWorldBankCountries <- function(){
        require(RJSONIO)
        wbCountries <-
                fromJSON("http://api.worldbank.org/countries?per_page=12000&format=json") 
        wbCountries <- data.frame(t(sapply(wbCountries[[2]], unlist)))
        wbCountries$longitude <- as.numeric(wbCountries$longitude)
        wbCountries$latitude <- as.numeric(wbCountries$latitude)
        levels(wbCountries$region.value) <- gsub(" \\(all income levels\\)",
                                                 "", levels(wbCountries$region.value))
        return(wbCountries)
}
```

##Next slide
```{r, cache=TRUE}
library(RJSONIO)
## Create a string 1960:this year, e.g. 1960:2011
years <- paste("1960:", format(Sys.Date(), "%Y"), sep="")

## Fertility rate
fertility.rate <- getWorldBankData(id='SP.DYN.TFRT.IN', date=years, value="fertility.rate")

## Life Expectancy
life.exp <- getWorldBankData(id='SP.DYN.LE00.IN', date=years,value="life.expectancy") 

## Population
population <- getWorldBankData(id='SP.POP.TOTL', date=years, value="population")

## GDP per capita (current US$)
GDP.per.capita <- getWorldBankData(id='NY.GDP.PCAP.CD',date=years,value="GDP.per.capita.Current.USD") 

## Merge data sets
wbData <- merge(life.exp, fertility.rate)
wbData <- merge(wbData, population)
wbData <- merge(wbData, GDP.per.capita)

## Get country mappings
wbCountries <- getWorldBankCountries()

## Add regional information
wbData <- merge(wbData, wbCountries[c("iso2Code", "region.value", "incomeLevel.value")],by.x="country.id", by.y="iso2Code")

```

###Step 2: Build the Motion Chart
```{r, warning=FALSE, error=FALSE }

subData <- subset(wbData, !region.value %in% "Aggregates" , select=
                  -country.id) 
## Create a motion chart
suppressPackageStartupMessages(library(googleVis))
library(googleVis)

M <- gvisMotionChart(subData, idvar="country.name", timevar="year",
                     options=list(width=700, height=600))

## Display the chart in your browser
plot(M)
```

